### 2021-09-01 README.Rmd

**NOTE**: The full pipeline will take a *very long* time to run.  I suggest switching off individual-level random effects (more details in comments in `_targets.R`) if you want to run the project on your own computer.  Without individual-level random effects the pipeline should run relatively quickly (< 1hr, I think).

**Using HPC**:
Also, you may need to install packages on the remote HPC if using `tar_make_clustermq()` with the SSH option.  Unfortunately, I'm not sure if there is an easy way to do this using `renv`. You should, however, make sure the same versions of the packages are installed locally and on the HPC, especially `gratia` which I'm using a development version of that has important bugs fixed, but not new bugs introduced.

>>>>

**Using HPC**:
You may need to install packages on the remote HPC if using `tar_make_clustermq()` with the SSH option.  Unfortunately, I'm not sure if there is an easy way to do this using `renv`. You should, however, make sure the same versions of the packages are installed locally and on the HPC, especially `gratia` which I'm using a development version of that has important bugs fixed, but not new bugs introduced.
